Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-07-11 README.Rmd
Updated readme with instructions

```{r time, eval=TRUE, echo=FALSE, message=FALSE, fig.width=10.5, fig.height=8.5}
source("utils/multi_plot.R")
source("utils/time_plot.R")
theme_set(theme_classic())
p1 <- history_box() + theme(text=element_text(family='Palatino'))
p2 <- future_box() + theme(text=element_text(family='Palatino'))
multi_plot(p1, p2, cols=2)
```

>>>>

```{r time, eval=TRUE, echo=FALSE, message=FALSE, fig.width=10.5, fig.height=8.5}
source("utils/multi_plot.R")
source("utils/time_plot.R")
theme_set(theme_classic())
p1 <- history_box()
p2 <- future_box()
multi_plot(p1, p2, cols=2)
```

## To run the simulations

In R, install packages and load them to ensure they installed.

```
install.packages("devtools")
install.packages("igraph")
install.packages("ggplot2")
install.packages("rstan")
install.packages("shinystan")
install.packages("dplyr")
install.packages("tidyr")
install.packages("magrittr")
install.packages("purrr")
install.packages("stringr")
install.packages("tseries")
install.packages("lhs")

devtools::install_github("JohnNay/sa")
library(igraph)
library(ggplot2)
library(rstan)
library(shinystan)
library(dplyr)
library(tidyr)
library(magrittr)
library(purrr)
library(stringr)
library(tseries)
library(lhs)
```

Then in R source the main simulation model file and test it out for a run with randomly chosen parameters.

```
source("main.R")
main(c(runif(3, min = 0.0001, max = 0.9999), 1, runif(2, min = 0.0001, max = 0.9999)), visu =T)
```

In the terminal run the following to conduct a sensitivity analysis simulation experiment with 8 cores. The only argument to this script is the number of cores to use.

```
Rscript master.R 8 &
```

In the terminal run the following to conduct the time series experiment with 8 cores. The only argument to this script is the number of cores to use.

```
Rscript master_timeseries_experiments.R 8 &
```
